---
title: "Lab 8"
author: "Corinna Hong"
date: "November 21, 2018"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}

library(tidyverse)

```

```{r, include = FALSE}

salmon <- read_csv("salmon.csv")

```

### Exploratory Graph

```{r, echo = FALSE}

# Exploratory graph

salmon_scatter <- ggplot(salmon, aes(x = Year, y = Salmon_vol)) +
  geom_point()
salmon_scatter

# Overall the data looks linear. There are some outliers that fall outside of linear, but I think a linear regression is ok

```

### Linear Regression

```{r, echo = FALSE, include = FALSE}

# Liner regression in R

salmon_model <- lm(Salmon_vol ~ Year, data = salmon)
salmon_model

```

U.S. Annual Import = 7550*(Year) - 14982940 tons

Slope: About 7550 tons of salmon are imported per year

y-int: About -14982940 tons of salmons was imported in year 0. This is concerning because at a certain x year, the imports will start being negative.

### Model Diagnostics

```{r, echo = FALSE}

# Model diagnostics

par(mfrow = c(2,2))
plot(salmon_model)

```

Residuals look normally distributed with a few outliers, but they are not enough to cause concern about violating homoscedasticity

### Model fit and significance

```{r, include = FALSE}

# Detailed model information

summary(salmon_model)

```

R^2^ = 0.9478, p for model fit < 0.001

Basd on this model, year significanly predicts salmon imports. R^2^ is the proportion of the variance in salmon imports that is explained by year. 95% of variance in salmon imports is predictable by year and 15% of variance in salmong imports is not predictable by year.

### Final graph

```{r, echo = FALSE}

salmon_final_graph <- ggplot(salmon, aes (x = Year, y = Salmon_vol)) +
  geom_point() +
  geom_smooth(method = lm, size = 0.5, color = "grey30") + # 95% CI default, se = true default (puts CI around smooth)
  theme_classic() +
  scale_x_continuous(expand = c(0,0), limits = c(1990, 2017)) +
  labs(x = "Year", y = "U.S. Annual Salmon Imports\n(1,000 pounds)")
salmon_final_graph

```

### Predictions using model

```{r, echo = FALSE}

# New data frame containing years we want to predict for

new_years <- data.frame(Year = c(2022, 2024, 2026, 2028))


# Feed new data frame into predict() function

future_predict <- predict(salmon_model, newdata = new_years, interval = "confidence") # interval = "confidence" to report lower and upper bounds of 95% CI.


# merge them into one df

predictions <- data.frame(new_years, future_predict)
predictions

```

### Pearson's *r*

```{r, include = FALSE}

# H0: Correlation equals 0
# HA: Correlation does not equal 0

salmon_pearsons <- cor.test(salmon$Year, salmon$Salmon_vol)
salmon_pearsons

```

t(26) = 21.723, p < 0.001. Reject the null. Correlation equals 0.97, which is a strong positive correlation.

### Final statement

Year significantly predicts U.S. annual import of salmon (*b* = 7550, t(`r salmon_pearsons$parameter`) = `r round(salmon_pearsons$statistic, 2)`, *p* < 0.001) with a strong positive correlation between the two (Pearson's *r* = `r round(salmon_pearsons$estimate, 2)`). The overall model (Imports = 7550(year) - 14982940, imports measured in tons) explains a significant amount of variance in U.S. imports (F(1,26) = 471.9, *p* < 0.001, R^2^ = 0.9478).