---
title: "Lab 8"
author: "Corinna Hong"
date: "November 21, 2018"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}

library(tidyverse)

```

```{r, include = FALSE}

salmon <- read_csv("salmon.csv")

```

### Exploratory Graph

```{r, echo = FALSE}

# Exploratory graph

salmon_scatter <- ggplot(salmon, aes(x = Year, y = Salmon_vol)) +
  geom_point()
salmon_scatter

# Overall the data looks linear. There are some outliers that fall outside of linear, but I think a linear regression is ok

```

### Linear Regression

```{r, echo = FALSE}

# Liner regression in R

salmon_model <- lm(Salmon_vol ~ Year, data = salmon)
salmon_model

```

Import = 7550*(Year) - 14982940 tons

Slope: About 7550 tons of salmon are imported per year

y-int: About -14982940 tons of salmons was imported in year 0. This is concerning because at a certain x year, the imports will start being negative.

### Model Diagnostics

```{r, echo = FALSE}

# Model diagnostics

par(mfrow = c(2,2))
plot(salmon_model)

```

Residuals look normally distributed with a few outliers, but they are not enough to cause concern about violating homoscedasticity

### Model fit and significance

```{r, include = FALSE}

# Detailed model information

summary(salmon_model)

```

R^2^ = 0.9478, p for model fit < 0.001

Basd on this model, year significanly predicts salmon imports. R^2^ is the proportion of the variance in salmon imports that is explained by year. 95% of variance in salmon imports is predictable by year and 15% of variance in salmong imports is not predictable by year.

### Final graph

```{r}

salmon_final_graph <- ggplot(salmon, aes (x = Year, y = Salmon_vol)) +
  geom_point() +
  geom_smooth(method = lm, se = TRUE, size = 0.5, color = "grey20") +
  theme_classic()
salmon_final_graph

```

